---
title: "Content Platform Pulse Check"
date: "`r format(Sys.Date()-(as.POSIXlt(Sys.Date())$wday+2), '%B %d, %Y')`"
output:
  html_document:
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.height = 3.4,
  warning = FALSE,
  message = FALSE
)
```

```{r echo=FALSE, eval=FALSE}
# Run this to get the token and save it in a file, must be run interactively.
# This gets added to /var/credentials via a custom secret associated with the
# pipeline.
token <- gs_auth()
saveRDS(token, file = "googlesheets_token.rds")
```

```{r results="hide"}
library(ggplot2)
library(googlesheets)
library(knitr)
library(lubridate)
library(dplyr)
library(gridExtra)
library(scales)

gs_auth(token="/var/credentials/googlesheets_token.rds")
sheetRef <- gs_url("https://docs.google.com/spreadsheets/d/1-SWzwxHWl3gh08xJOa3P_gyNMsUw5ufwSvQMyrdTi5c")
CPPulse <- gs_read(ss=sheetRef, ws="Form Responses 1")

CPPulse$Date <- as.Date(CPPulse$Timestamp, format="%m/%d/%Y")
CPPulse$Week <- floor_date(CPPulse$Date, "week")
colnames(CPPulse) <- c("Timestamp", "Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Other", "Feedback", "Shoutouts", "Date", "Week")

CPPulseLastWeek <- CPPulse[CPPulse$Week == max(CPPulse$Week),]
```

```{r}
colorScale <- c("#ffffff", "#ee1c25", "#f26724", "#f8c611", "#84c341", "#33a94b")
names(colorScale) <- c("0", "1", "2", "3", "4", "5")
displayPlot <- function(qnum) {
  CPPulse$Q <- CPPulse[[qnum]]
  CPPulseLastWeek$Q <- CPPulseLastWeek[[qnum]]
  plot1 <- CPPulse %>% group_by(Week, Q) %>% summarize(cnt=n()) %>%
    ggplot(aes(x=Week, y=Q, size=cnt, color=factor(Q, levels=c(1,2,3,4,5)))) +
      geom_point() +
      geom_smooth(color="#4166ef") +
      guides(color=F, size=F) +
      ylab("Score") +
      scale_y_continuous(limits=c(0, 5.3), oob=rescale_none, breaks=c(1:5), minor_breaks=NULL) +
      scale_color_manual(values=colorScale)
  plot2 <- CPPulseLastWeek %>% group_by(Q) %>% summarize(cnt=n()) %>%
    ggplot(aes(x=Q, y=cnt, fill=factor(Q))) +
      geom_bar(stat="identity", width=0.5) +
      xlab("") +
      ylab("This week") +
      coord_flip() +
      guides(color=F, fill=F) +
      scale_x_continuous(limits=c(0, 5.3), oob=rescale_none, breaks=c(1:5), minor_breaks=NULL) +
      scale_y_continuous(breaks=c(1:(max(CPPulseLastWeek$Q)+2)), minor_breaks=NULL) +
      scale_fill_manual(values=colorScale)
  grid.arrange(plot1, plot2, ncol=2, widths=c(300, 100))
}
```

Hi team,

Here is last week's team pulse survey. As always, please send any questions to me, Emily, or Anthony.

#### Shout-outs from this week:

```{r,results='asis'}
prevfriday <- function(x) 7 * floor(as.numeric(x-5+4) / 7) + as.Date(5-4, origin = "1970-01-01")
tbl <- CPPulse[!is.na(CPPulse$Shoutouts) & CPPulse$Date >= prevfriday(Sys.Date()),]
for (text in tbl$Shoutouts) {
  cat(gsub(pattern = "\n", replacement = "  \n", x = text))
  cat("  \n")
}
```

#### Q1: I feel good about this week in general

```{r}
displayPlot("Q1")
```

#### Q2: I feel good about the Content Platform initiative this week

```{r}
displayPlot("Q2")
```

#### Q3: I worked sustainably this week

```{r}
displayPlot("Q3")
```

#### Q4: I'm excited about what we're doing in this initiative and my role in it

```{r}
displayPlot("Q4")
```

#### Q5: I understand how strategic/tactical decisions for this initiative are made

```{r}
displayPlot("Q5")
```

#### Q6: I feel like this initiative's leads have been communicative and supportive enough

```{r}
displayPlot("Q6")
```
